JD notes on effects

### 2022-06-27 manuscript/body.tex
Big RSA arrival merge

In an ordinary linear model, the link function $g$ is the identity function, so the two means are the same. For non-trivial links, we expect them to be different in general. 
\jd{What are the key ideas if any from the rest of this \P?}. I would like to clearly describe what happens with the log link, and also what happens near each end in a logit link. Why is this a place to talk about the explicit Taylor?}
strictly concave or strictly convex, one can use Jensen's inequality to determine which side of Equation~\ref{eq:compare_anchored_pop_based} is decelerating or accelerating. For accelerating functions, the Jensen’s inequality describes how the changes in input values elevate the predictions and otherwise describes how these changes depress the predictions. For a non-fully convex or concave link function, one can use Taylor series expansion to approximate the range over which the two are smaller or smaller than the other and then apply second-order approximation \citep{hanmer2013behind}.

@@

\jd{What does this mean? I was going to say that $g$ collapses out of \eqref{compare_anchored_pop_based} and the results are identical. Is that wrong?} As stated above, in simple linear models without interactions, the effect is constant, so both approaches yield similar results. 
However, picking a single value, e.g., mean of the predictor, on which to draw conclusions about the effect can be problematic, unrealistic or not contained in or representative of the population. In addition, the mean-based approach fails to use every values of non-focal predictors hence not utilizing the full potential of the information contained in the data. This may limit the inferences we can make about the entire population. In general, the mean-based approach provides the predictions of an average case, whereas the whole-sample-based approach, summarizes the predictions over the entire population. In some applications, the effect of an average case might not be generalizable to the entire population, especially, if the average does not represent the population. This is might not be a problem in whole-sample-based approach since it focuses on specific observations because the prediction is first obtained for each observation and then averaged across the levels of the focal input variable.

>>>>

In an ordinary linear model, the link function $g$ is the identity function, so the two means are the same. For non-trivial links, we expect them to be different in general. 
\jd{What are the key ideas if any from the rest of this \P?. I would like to clearly describe what happens with the log link, and also what happens near each end in a logit link. Why is this a place to talk about the explicit Taylor?}
strictly concave or strictly convex, one can use Jensen's inequality to determine which side of Equation~\ref{eq:compare_anchored_pop_based} is decelerating or accelerating. For accelerating functions, the Jensen’s inequality describes how the changes in input values elevate the predictions and otherwise describes how these changes depress the predictions. For a non-fully convex or concave link function, one can use Taylor series expansion to approximate the range over which the two are smaller or smaller than the other and then apply second-order approximation \citep{hanmer2013behind}.

@@

\jd{What does this mean? I was going to say that $g$ collapses out of \eref{compare_anchored_pop_based} and the results are identical. Is that wrong?} As stated above, in simple linear models without interactions, the effect is constant, so both approaches yield similar results. 
However, picking a single value, e.g., mean of the predictor, on which to draw conclusions about the effect can be problematic, unrealistic or not contained in or representative of the population. In addition, the mean-based approach fails to use every values of non-focal predictors hence not utilizing the full potential of the information contained in the data. This may limit the inferences we can make about the entire population. In general, the mean-based approach provides the predictions of an average case, whereas the whole-sample-based approach, summarizes the predictions over the entire population. In some applications, the effect of an average case might not be generalizable to the entire population, especially, if the average does not represent the population. This is might not be a problem in whole-sample-based approach since it focuses on specific observations because the prediction is first obtained for each observation and then averaged across the levels of the focal input variable.
